### 2017-01-20 slides/figures/gan_conceptual.tex
fixed font size in GAN

\begin{document}
\usetikzlibrary{arrows.meta}
% why does the figure seems to have lots of whitespace to the left when shapes[.symbols] is included??
%\usetikzlibrary{shapes.symbols}
%\tikzstyle{c} = [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1,gb]
\tikzstyle{gb} = [draw,outer sep=7,inner sep=7,minimum size=57,line width=1, very thick, draw=black!55, top color=white,bottom color=black!20]
\tikzstyle{cloud} = [draw, circle, node distance=2.5cm, minimum height=2em, gb]
\tikzstyle{arr} = [thick,-{Latex[length=3mm,width=2mm]}]
\begin{tikzpicture}

% latent space
\node[circle,gb] (latent_space) {Random Noise};

% nodes
\node [gb] (generator) at ([shift={(5,0)}] latent_space) {Generator $G$};
  \node [cloud] (data) at ([shift={(0,4)}] generator) {\Large $X$};

\node [gb] (discriminator) at ([shift={(5,2)}] generator) {Discriminator $D$};
  \node[gb,dashed] (loss) at ([shift={(5,0)}] discriminator) {Loss $\mathcal{L}$};

% flow
\draw[arr] (latent_space) -- (generator) node[midway,label=below:sample] {};
\draw[arr] (generator) -- (discriminator) node[midway,label=below:generate] {};
\draw[arr] (data) -- (discriminator) node[midway,pos=0.4,label=below:sample] {};
\draw[arr] (discriminator) -- (loss) node[midway,label=below:Real/Fake] {};

% gradient flow
\path[dashed,arr] (loss) edge[bend right] node [label=$\nabla \mathcal{L}$ with regard to $D$] {} (discriminator);
\path[dashed,arr] (loss) edge[bend left] node [label=below:$\nabla \mathcal{L}$ with regard to $G$] {} (generator);

>>>>

\usetikzlibrary{arrows.meta}

\begin{document}
% why does the figure seems to have lots of whitespace to the left when shapes[.symbols] is included??
%\usetikzlibrary{shapes.symbols}
%\tikzstyle{c} = [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1,gb]
\tikzstyle{gb} = [draw,outer sep=7,inner sep=7,minimum size=57,line width=1, very thick, draw=black!55, top color=white,bottom color=black!20]
\tikzstyle{cloud} = [draw, circle, node distance=2.5cm, minimum height=2em, gb]
\tikzstyle{arr} = [thick,-{Latex[length=3mm,width=2mm]}]
\begin{tikzpicture}

% latent space
\node[circle,gb] (latent_space) {\large Random Noise};

% nodes
\node [gb] (generator) at ([shift={(5,0)}] latent_space) {\large Generator $G$};
  \node [cloud] (data) at ([shift={(0,4)}] generator) {\Large $X$};

\node [gb] (discriminator) at ([shift={(5,2)}] generator) {\large Discriminator $D$};
  \node[gb,dashed] (loss) at ([shift={(5,0)}] discriminator) {\large Loss $\mathcal{L}$};

% flow
\draw[arr] (latent_space) -- (generator) node[midway,label=below:\large sample] {};
  \draw[arr] (generator) -- (discriminator) node[midway,pos=0.7,label=below:\large generate] {};
\draw[arr] (data) -- (discriminator) node[midway,pos=0.4,label=below:\large sample] {};
\draw[arr] (discriminator) -- (loss) node[midway,label=below:\large real/fake] {};

% gradient flow
\path[dashed,arr] (loss) edge[bend right] node [label=\large $\nabla \mathcal{L}$ with regard to $D$] {} (discriminator);
\path[dashed,arr] (loss) edge[bend left] node [label=below:\large $\nabla \mathcal{L}$ with regard to $G$] {} (generator);
